Title here

### 2016-08-24 portfolio/text/ms.Rmd
Copy editing text

Individuals relying on natural resources as their primary source of income
often experience highly variable income levels 
due to the combined effects of environmental and price variation. 
Commercial fishers are a prime example and
recent work has sought to identify regulations and fishing behaviours 
that can reduce this variability. 
A top candidate has been that fishing higher levels of species diversity
decreases income variability.
However, it is unknown if this species-diversity effect 
on income variability holds 
across multiple approaches to diversifying catch,
at the level of individual permit holders,
and across different fishing strategies. 
Here, we simultaneously estimate the effects of three 
methods of diversification for Alaskan fishery permit holders
on revenue and revenue variability:
(1) owning multiple permits, 
(2) owning permits that inherently fish higher species diversity, 
and (3) adjusting species diversity within the constraints of a permit.
We control for changes in effort and other 
residual effects through time.
We find that 
fishing an additional permit is associated with 
lower variability (~XX--XX%) and higher revenue,
fishing permits with higher species diversity reduces risk 
(XX--XX% per unit increase in Simpson's diversity index),
but that changing species diversity within a
permit's constraints has a fishery-dependent effect on revenue and 
is usually (XX%) associated with increased revenue variability.
At the same time, Alaskan commercial fisheries
have increasingly focussed on 
single-permit (often salmon) fishing strategies
with single-permit fishers earning 
more than multiple-permit fishers
for the first time in 2014.
Our results suggest that the benefit of species diversity
on reducing revenue variability 
is mostly an across-permit effect, not
a benefit that can be easily harnessed by an individual permit holder.
Effective methods of diversification --- 
purchasing additional permits or switching permits ---
are costly and often limited by regulations such as limited entry
programs and individual transferable quotas (ITQs).
Take home ...

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Diversifying permits reduces risk and usually increases revenue.
Two examples of expected revenue variability 
and median revenue for
owners of (A) individual halibut and (B) gillnet herring roe permits
(light blue)
compared with owners of the same permit plus one more (medium blue)
or two more permits (dark blue).
On the y-axis, dots and lines represent posterior median and 50\%
credible intervals.}
\label{fig:spokes}
\end{center}
\end{figure}

>>>>

Individuals relying on natural resources as their primary source of income
often experience high levels of income variability 
due to the combined effects of environmental and price variation. 
Commercial fishers are a prime example and
recent work has sought to identify regulations and fishing behaviours 
that can reduce this variability. 
A top candidate has been that fishing higher levels of species diversity
decreases income variability.
However, it is unknown if this species-diversity effect 
on income variability holds 
across multiple approaches to diversifying catch,
at the level of individual permit holders,
and across different fishing strategies. 
Here, we simultaneously estimate the effects of three 
methods of diversification for Alaskan fishery permit holders
on revenue and revenue variability:
(1) owning multiple permits, 
(2) owning permits that inherently fish higher species diversity, 
and (3) adjusting species diversity within the constraints of a permit.
We control for changes in effort and other 
residual effects through time.
We find that 
fishing an additional permit is associated with 
lower variability (~XX--XX%) and higher revenue,
fishing permits with higher species diversity reduces risk 
(XX--XX% per unit increase in Simpson's diversity index),
but that changing species diversity within a
permit's constraints has a fishery-dependent effect on revenue and 
is usually (XX%) associated with increased revenue variability.
At the same time, Alaskan commercial fisheries
have increasingly focussed on 
single-permit (often salmon) fishing strategies
with single-permit fishers earning 
more than multiple-permit fishers
since 2013.
Our results suggest that the benefit of species diversity
on reducing revenue variability 
is mostly an across-permit effect, not
a benefit that can be easily harnessed by an individual permit holder.
Effective methods of diversification --- 
purchasing additional permits or switching permits ---
are costly and often limited by regulations such as limited entry
programs and individual transferable quotas (ITQs).
Take home ...

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}
\caption{Diversifying permits reduces risk and usually increases revenue.
Two examples of expected revenue variability 
and median revenue for
owners of (A) individual halibut and (B) gillnet herring roe permits
(light blue)
compared with owners of the same permit plus one more (medium blue)
or two more permits (dark blue).
On the y-axis, dots and lines represent posterior median and 90\%
credible intervals.}
\label{fig:spokes}
\end{center}
\end{figure}
